The extended light profiles of the Sculptor and Ursa Minor dwarf galaxies: Innate nature or tidal nurture?

### 2025-10-21 thesis/main.tex
julio final edits

\title{
    The extended light profiles of the Sculptor and Ursa Minor dwarf galaxies: Nature or tidal nurture?
}
\author{Daniel A. Boyea}

@@

       \@author\\
       B.Sc. The Ohio State University, 2023\\
       \vspace*{3\baselineskip}
    A Thesis Submitted in Partial Fulfillment of the Requirements for the Degree of\\
    \skipline

@@

    in the Department of Physics and Astronomy\\
       \vfill
       {\small
       ©\@author, 2025\\
       University of Victoria\\
   }
   \skipline
       {\small
       All rights reserved. This thesis may not be reproduced in whole or in part,
   by photocopy or other means, without the permission of the author.} \\
\skipline
   \end{center}
We acknowledge and respect the \Lekwnen{} (Songhees and X\textsuperscript{w}seps\schwa{}m/
Esquimalt) Peoples on whose territory the university stands, and the
\Lekwnen{} and ${\underaccent{\bar}{\rm W}}$S\'ANE\'C Peoples whose historical relationships with the
land continue to this day. 
\end{titlepage}

@@

\addcontentsline{toc}{chapter}{Supervisory Committee}
\begin{centering}
\textbf{\@title}\\
\skipline
by\\
\skipline
\@author\\
B.Sc. The Ohio State University, 2023\\
\vspace*{3\baselineskip}
\end{centering}

@@

\noindent Dr. Kim Venn\\
Department of Astronomy\\

\skipline

\noindent External Examiner \\
Outside Department

@@

\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
\input{acknowledgments}

%% Lists
%\chapter*{Symbols}
%
%
%\setlength{\tabcolsep}{0pt}
%\begin{longtable}{p{0.2\textwidth} p{0.8\textwidth}}
%$\rho$ & 3-dimensional mass density. \\
%
%$\Sigma$ & 2-dimensional density \\
%\end{longtable}
%
%\setlength{\tabcolsep}{6pt}
%\renewcommand*{\arraystretch}{1}
%
%
%\printglossary[type=\acronymtype,nonumberlist]
%\printglossary
%
%
\newpage

\thispagestyle{empty}
\renewcommand{\epigraphflush}{center}
\vfill
\setlength{\epigraphwidth}{0.5\textwidth}
\epigraph{The sun had fallen beneath the horizon in the east, and the long day was about to end. But tomorrow, the sun would rise in the west again, bathing the world in a kinder light.}{Baoshu, translation by Ken Liu}

\epigraph{
In the land of my birth, there is a hill, and upon that hill is a rock where I have sat and watched a changing world. This rock will not change, I would say. I'll pass from this Earth, but the rock will remain ever watchful of the land.

But my feet kicked the dirt beneath me. Were the granules of soil not once like this rock? Is the rock not a collection of their multitudes?

[We are] neither destroyed nor created, but a collection of dust meant to observe a changing world and then return to dust. 
}{Joe Fisher, {\it Midnight Burger}}
\vfill

@@

\chapter*{Research Acknowledgments}
\addcontentsline{toc}{chapter}{Research Acknowledgments}
\input{research_acknowledgments}

>>>>

\title{
    The extended light profiles of the Sculptor and Ursa Minor dwarf galaxies: Innate nature or tidal nurture?
}
\author{Daniel A. Boyea}

@@

       \@author\\
       Bachelor of Science, The Ohio State University, 2023\\
       \vspace*{3\baselineskip}
    A Thesis Submitted in Partial Fulfillment of the Requirements for the Degree of\\
    \skipline

@@

    in the Department of Physics and Astronomy\\
       \vfill
       {\small
       ©\@author, 2025\\
       University of Victoria\\
   }
   \skipline
       {\small
       All rights reserved. This thesis may not be reproduced in whole or in part,
   by photocopy or other means, without the permission of the author.} \\
\skipline
   {\small
We acknowledge and respect the \Lekwnen{} (Songhees and X\textsuperscript{w}seps\schwa{}m/
Esquimalt) Peoples on whose territory the university stands, and the
\Lekwnen{} and ${\underaccent{\bar}{\rm W}}$S\'ANE\'C Peoples whose historical relationships with the
land continue to this day. 
}
   \end{center}

\end{titlepage}

@@

\phantomsection
\addcontentsline{toc}{chapter}{Supervisory Committee}
\begin{centering}
\textbf{\@title}\\
\skipline
by\\
\skipline
\@author\\
Bachelor of Science, The Ohio State University, 2023\\
\vspace*{3\baselineskip}
\end{centering}

@@

\noindent Dr. Kim Venn, Departmental Member\\
Department of Astronomy\\

@@

\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
\input{acknowledgements}

%% Lists
%\chapter*{Symbols}
%
%
%\setlength{\tabcolsep}{0pt}
%\begin{longtable}{p{0.2\textwidth} p{0.8\textwidth}}
%$\rho$ & 3-dimensional mass density. \\
%
%$\Sigma$ & 2-dimensional density \\
%\end{longtable}
%
%\setlength{\tabcolsep}{6pt}
%\renewcommand*{\arraystretch}{1}
%
%
%\printglossary[type=\acronymtype,nonumberlist]
%\printglossary
%
%
\newpage
\thispagestyle{empty}

\renewcommand{\epigraphflush}{center}
\phantomsection
\addcontentsline{toc}{chapter}{Epigraph}
       \vspace*{6\baselineskip}
\setlength{\epigraphwidth}{0.5\textwidth}
%\epigraph{The sun had fallen beneath the horizon in the east, and the long day was about to end. But tomorrow, the sun would rise in the west again, bathing the world in a kinder light.}{Baoshu, translation by Ken Liu}

\epigraph{
In the land of my birth, there is a hill. And upon that hill is a rock where I have sat and watched a changing world. This rock will not change---I would say. I'll pass from this Earth but the rock will remain, ever watchful of the land.
But my feet kicked the dirt beneath me. Were the granules of soil not once like this rock? Is the rock not a collection of their multitudes? \ldots\ And is my path so different? Neither destroyed nor created, but a collection of dust meant to observe a changing world and then return to dust. 
}{---Joe Fisher, {\it Midnight Burger}}

@@

\chapter*{Research Acknowledgments}
\addcontentsline{toc}{chapter}{Research Acknowledgments}
\input{research_acknowledgements}
